---
title: "Stats Homework 2"
output: pdf_document
---

# ANOVA 

As an SE researcher you are evaluating different programming languages. For the next set of questions input the R code and interpret your findings.

```{r setup, echo=T, results='hide', error=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy.opts = list(width.cutoff = 60), tidy = TRUE)

library(Sleuth3) # example datasets from textbook, "The Statistical Sleuth - A Course in 
# Methods of Data Analysis (3rd Edition)"
library(reshape2) # for formatting and aggregation of data frames
library(ggplot2) # for creating graphs
library(dplyr) # for data manipulation and clean-up
library(plotly) # for creating interactive web graphics from ggplot2 graphs
library(knitr) # required for generating PDF output
library(modeest) # required for `mfv()` function
library(nortest)
library(reshape2)

```

a) The results of your first study compares Java, Python, and Ruby code based on the size of the programs in source (i.e. non-blank, non-commented) lines of code. Perform an ANOVA to determine whether there is an effect on size due to programming language. Use `lang-size.csv`. 

```{r}

Hw2Data1 <- read.csv("lang-size.csv")
Hw2Data1


Hw2model1 <- aov(Hw2Data1$sloc ~ Hw2Data1$lang)
summary(Hw2model1)


TukeyHSD(Hw2model1)



```
Report:


b) In a subsequent study you measured the programming time (in hours) required to solve a program in Java, Python, and Ruby. This was a within subject study design: each participant solved the problem three times, and all participants solved the problem in the same order (Java, then Python, then Ruby). Perform an ANOVA to determine whether there is an effect due to programming language. Use `lang-time.csv`.

```{r}

Hw2Data2 <- read.csv("lang-time.csv")
Hw2Data2


Hw2model2 <- aov(Hw2Data2$times ~ Hw2Data2$lang + Hw2Data2$participant)
summary(Hw2model2)


TukeyHSD(Hw2model2)



```
Report:


c) Your realized you should have counterbalanced, so you replicated the study from (b) which uses a crossover design to control for ordering. Each participant solved the problem in all three languages, but in each participant solved them in a different order. Perform an ANOVA to determine whether there is an effect due to programming language. Use `lang-time-crossover.csv`. 

```{r}
# Reading the file 
Hw2Data3 <- read.csv("lang-time-crossover.csv")
Hw2Data3




```
Report:

d) You have some simulated results from an experiment that compared development time for Java, Python and Ruby, for subjects with low experience and high experience. Perform an ANOVA and identify which factors (language, experience) had a statistically significant effect. Also specify whether the interaction between programming language and experience was statistically significant or not. Use `lang-time-exp.csv`. 

```{r}

Hw2Data4 <- read.csv("lang-time-exp.csv")
Hw2Data4

Hw2model4 <- aov(Hw2Data4$times ~ Hw2Data4$lang + Hw2Data4$exp)
summary(Hw2model4)

```
Report:

# Part 2: Data analysis of an experiment

In this question, you'll analyze the raw data from an experiment and write up the results (similar to a publication).

The data is from a experiment to test whether statically typed languages (e.g. Java) or dynamically typed languages (e.g. Python) require more programming effort. The study evaluates the languages on two problems, a "small" problem and a "large" problem, to see if the results change based on the size of the problem. The study is a factorial design. The raw data from the experiment is available in this file: `lang-time-size.csv`.

Analyze the data and write up a short "results" section (as if it were a part of a paper) with your analysis of the data. This section should contain:
* Box plots to show the raw data
* Analysis of variance tables to determine if there are any interactions
* Results of pairwise t-tests to test if the factors that you may see significance truly have an effect
* Interaction plot between the 2 factors 
* Effect sizes for programming language for the "small" problem and for the "large" problem.
* I am not looking for a specific format, use your judgement about the best way to present this data to convey the results to a reader. 

```{r}
# Code for analysis goes here.
```